Measuring E-Mail Header Injections on the World Wide Web

### 2016-10-24 Background/history.tex
almost at 13 pages, need to bering it to 9

We found the first \ehi description in a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how an \ehi vulnerability existed in the implementation of the \texttt{mail()} function in PHP and how it can be exploited. More recently, a blog post by Damon Kohler~\cite{DK} and an accompanying wiki article~\cite{Injection} describe the attack vector and outline few defense measures for \ehi vulnerabilities.

>>>>

We found the first \ehi description in a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo| describing how an \ehi vulnerability existed in the implementation of the \texttt{mail()} function in PHP and how it can be exploited. More recently, a blog post by Damon Kohler~\cite{DK} and an accompanying wiki article~\cite{Injection} describe the attack vector and outline few defense measures for \ehi vulnerabilities.

### 2016-10-24 Background/impact.tex
fixed some small things Fixed all todos till sys design
almost at 13 pages, need to bering it to 9

\noindent\textbf{Information Extraction}
	\emails can contain sensitive data that is meant to be accessed only by the user. Due to an \ehi vulnerability, an attacker can add a \texttt{bcc} header, and the \email server will send a copy of the private \email to the attacker, thereby extracting important information.
	User privacy can thus be compromised, and loss of private information can by itself lead to other attacks.

>>>>

\noindent\textbf{Information Extraction}
	\Emails can contain sensitive data that is meant to be accessed only by the user. Due to an \ehi vulnerability, an attacker can add a \texttt{bcc} header, and the \email server will send a copy of the \email to the attacker, thereby exposing important information.
	User privacy can thus be compromised, and loss of private information can by itself lead to other attacks.

### 2016-10-24 Background/lang_aff.tex
almost at 13 pages, need to bering it to 9

\subsection{Languages Affected}
\label{languages}
This section describes the popular programming languages that contain \ehi vulnerabilities in their standard email libraries. This section is not intended as a complete reference of vulnerable functions and methods, but rather as a guide that specifies which parts of the language are vulnerable.

@@

After 13 further iterations of PHP since the 4.0 release (the current version is 7.1), the \texttt{mail()} function is yet to be fixed after 15 years. However, it is specified in the PHP documentation~\cite{PHPDocs} that the \texttt{mail()} function does not protect against \ehi.
A working code sample of the vulnerability, written in PHP~5.6 (latest well-supported version), is shown in  Listing~\ref{code:phpemi}.

@@

Unfortunately, the bug fix was only for the \texttt{email.header} package, and thus exists in other frequently used packages such as \texttt{email.parser}, where both the classic \texttt{Parser()} and the newer \texttt{FeedParser()} contain \ehi vulnerabilities even in the latest versions: \texttt{2.7.11} and \texttt{3.5}. The bug fix was also not backported to older versions of Python.
There is no mention of the vulnerability in the Python documentation for either library. Contrary to PHP's behavior of overwriting existing headers, Python only recognizes the first occurrence of a header, and ignores duplicate headers.
A working code sample of the vulnerability, written in Python 2.7.11, is shown in Listing~\ref{code:pyemi}.

>>>>

\subsection{Languages Affected}
\label{languages}
We now describe the popular programming languages that contain \ehi vulnerabilities in their standard \email libraries. This section is not intended as a complete reference of vulnerable functions and methods, but rather as a guide that specifies which parts of the language are vulnerable.

@@

After 13 further iterations of PHP since the 4.0 release (the current version is 7.1), the \texttt{mail()} function is yet to be fixed after 15 years. However, it is specified in the PHP documentation~\cite{PHPDocs} that the \texttt{mail()} function does not protect against \ehi.
A working code sample of the vulnerability, written in PHP~5.6 is shown in  Listing~\ref{code:phpemi}.

@@

Unfortunately, the bug fix was only for the \texttt{email.header} package, and not for other frequently used packages such as \texttt{email.parser}, where both the classic \texttt{Parser()} and the newer \texttt{FeedParser()} contain \ehi vulnerabilities even in the latest versions: \texttt{2.7.11} and \texttt{3.5}. The bug fix was also not backported to older versions of Python.
There is no mention of the vulnerability in the Python documentation for either library. Contrary to PHP's behavior of overwriting existing headers, Python only recognizes the first occurrence of a header, and ignores duplicate headers.
A working code sample of the vulnerability, written in Python 2.7.11, is shown in Listing~\ref{code:pyemi}.

### 2016-10-24 Background/ruby.tex
almost at 13 pages, need to bering it to 9

\begin{lstlisting}[language=Ruby,caption={Ruby program with e-mail
      header injection vulnerability.},label={code:rubyemi}, float]
require 'sinatra'
require 'net/smtp'

get '/hello' do
email = params[:email]

message = """
From: Sai <schand31@asu.edu>
Subject: SMTP e-mail test
To: #{email}

This is a test e-mail message.
"""
# construct a post request with email set to attack_string
# attack_string => sai@sai.com%0abcc:spc@spc.com%0aSubject:Hello
Net::SMTP.start('localhost', 1025) do |smtp|
smtp.send_message message, 'schand31@asu.edu',
'to@todomain.com'
end
# Headers get added, and Subject field changes to what we set.
end
\end{lstlisting}

>>>>

\begin{lstlisting}[language=Ruby,caption={Ruby program with e-mail
      header injection vulnerability.},label={code:rubyemi}, float]
require 'sinatra'
require 'net/smtp'
get '/hello' do
email = params[:email]
message = """
    From: Sch <sch@example.com>
    Subject: SMTP e-mail test
    To: #{email}

    This is a test e-mail message.
"""
# construct a post request with email set to attack_string
# attack_string => s@example.com%0abcc:spc@example.com%0aSubject:Hello
Net::SMTP.start('localhost',1025) do |smtp|
smtp.send_message message, 'sch@example.com', 'to@todomain.com'
end
# Headers get added, and Subject field changes to what we set.
end
\end{lstlisting}

### 2016-10-24 Discussion/limits.tex
almost at 13 pages, need to bering it to 9

		\begin{table}
			\centering
			\normalsize
			\begin{tabular}{|p{4cm}|c|c|}
				\hline
				\multicolumn{1}{|c}{\textbf{Method}} &
				\multicolumn{1}{|c|}{\textbf{Running time}} &
				\multicolumn{1}{|c|}{\textbf{Slowdown}}
				\\
				\hline
				\centering Using our pipeline & 629.043 & - \\
				\hline
				\centering Adding Selenium to our pipeline & 919.372 & \slowSelenium \\
				\hline				
				\centering Detecting \email fields by parsing each field instead of `grep'ing inside form & 707.154 & \slowParse \\								
				\hline
			\end{tabular}
			\caption[\titlecap{}]{Running times in seconds for crawling, parsing, and detecting presence of \email fields in 1000 random wikipedia pages.}
			\label{tab:perf}
		\end{table}

        Because we search for the words \texttt{e-mail}, \texttt{mail}, or \texttt{email} within the HTML form, if the website does not use English names for its forms our system will not be able to find the presence of an \email field. An example is shown in Listing~\ref{code:htmlfrench}. Here, the French word for \texttt{e-mail}---courrier électronique---is used, and our system is unable to find the presence of the e-mail field.

@@

\begin{lstlisting}[language=HTML,caption={e-mail field in a different language - French.},label={code:htmlfrench}, literate=%
	{é}{{\'e}}1, float]
<input type="text" 
placeholder="courrier électronique"
name="courrier_électronique">
\end{lstlisting}

>>>>

		\begin{table}
			\centering
			\normalsize
			\begin{tabular}{|p{4cm}|c|c|}
				\hline
				\multicolumn{1}{|c}{\textbf{Method}} &
				\multicolumn{1}{|c|}{\textbf{Running time}} &
				\multicolumn{1}{|c|}{\textbf{Slowdown}}
				\\
				\hline
				\centering Using our pipeline & 629.043 & - \\
				\hline
				\centering Our pipeline with Selenium & 919.372 & \slowSelenium \\
				\hline				
				\centering Parsing \email fields instead of `grep'ing inside form & 707.154 & \slowParse \\								
				\hline
			\end{tabular}
			\caption[\titlecap{}]{Running times in seconds for crawling, parsing, and detecting presence of \email fields in 1000 random wikipedia pages.}
			\label{tab:perf}
		\end{table}

        Because we search for the words \texttt{e-mail}, \texttt{mail}, or \texttt{email} within the HTML form, if the website does not use English names for its forms our system will not be able to find the presence of an \email field. An example is by using the French word for \texttt{e-mail}---courrier {{\'e}}lectronique--- our system is unable to find the presence of the e-mail field.

@@

%\begin{lstlisting}[language=HTML,caption={e-mail field in a different language - French.},label={code:htmlfrench}, literate=%
%	{é}{{\'e}}1, float]
%<input type="text" 
%placeholder="courrier électronique"
%name="courrier_électronique">
%\end{lstlisting}

### 2016-10-24 Discussion/mitigation.tex
updated for WWW paper
almost at 13 pages, need to bering it to 9

\subsection{Mitigation Strategy}
\label{disc:mitigation}
After demonstrating that \ehi vulnerabilities exist on the web at large, we now describe the most common measures that can be taken to prevent the occurrence of this vulnerability, or at least reduce the impact.
\begin{itemize}
	\item Use Mail Libraries\\
	Using a safe \email library is the preferred way of preventing \ehi vulnerabilities. Using a library that is well tested can remove the burden of input sanitization from the developer. 
	A list of known secure libraries for each language and framework discussed previously is shown in Table~\ref{tab:maillib}.

	Using libraries such as PEAR Mail, PHPMailer, Apache Commons E-Mail, Contact Form 7, and Swiftmailer can significantly reduce the occurrence of \ehi vulnerability.
	\begin{table}[tbp]
		\centering
		\begin{tabular}{|l|l|}
			\hline
			\multicolumn{1}{|c|}{\textbf{Language}} &
			\multicolumn{1}{c|}{\textbf{Mail Libraries}} \\
			\hline
			PHP & {{PEAR Mail\tablefootnote{PEAR Mail Website: https://pear.php.net/package/Mail}, PHPMailer\tablefootnote{PHPMailer Website:\\ https://github.com/PHPMailer/PHPMailer}, Swiftmailer\tablefootnote{Swiftmailer Website: http://swiftmailer.org/}}}\\
			\hline
			Python & SMTPLib with email.header.Header\tablefootnote{instead of using email.parser.Parser to parse the header}\\
			\hline
			Java & Apache Commons E-Mail\tablefootnote{Apache Commons E-Mail: https://commons.apache.org/proper/commons-email/}\\
			\hline
			Ruby & Ruby Mail \textgreater{}= 2.6\tablefootnote{Ruby Mail Website: https://rubygems.org/gems/mail}\\
			\hline
			WordPress & Contact Form 7\tablefootnote{Contact Form 7 Download: https://wordpress.org/plugins/contact-form-7/}\\
			\hline
		\end{tabular}
		\caption[\titlecap{Mail libraries that prevent e-mail header injection}]{Mail libraries that prevent e-mail header injection.}
		\label{tab:maillib}
	\end{table}
	\item Use a Content Management System (CMS) \\
	Content management systems such as WordPress and Drupal include libraries and plugins to prevent \ehi. Thus, websites built with such CMS' are usually resistant to these attacks. However, it is advised to use the correct \email plugin, as not all plugins might be secure.
	An example of a secure plug-in is included as part of Table~\ref{tab:maillib}.

	\item Input Validation\\
	If neither of the two options are feasible, due to reasons such as the website being an in-house production, or due to lack of support infrastructure, developers can choose to perform proper input sanitization. Sanitization should be done keeping in mind RFC5322~\cite{rfc5322}, and care must be taken to ensure that all edge cases are taken into account.

>>>>

\subsection{Mitigation Strategy}
\label{disc:mitigation}
After demonstrating that \ehi vulnerabilities exist on the web at large, we now describe the most common measures that can be taken to prevent the occurrence of this vulnerability, or at least reduce the impact.
\begin{itemize}
	\item Use Mail Libraries\\
	Using a safe, well tested \email library is the preferred way of preventing \ehi vulnerabilities (removing the burden of input sanitization from the developer). 
	A list of known secure libraries for each language and framework discussed is shown in Table~\ref{tab:maillib}.

	Using libraries such as PEAR Mail, PHPMailer, Apache Commons E-Mail, Contact Form 7, and Swiftmailer can significantly reduce the occurrence of \ehi vulnerability.
	\begin{table}[tbp]
		\centering
		\normalsize
		\begin{tabular}{|l|l|}
			\hline
			\multicolumn{1}{|c|}{\textbf{Language}} &
			\multicolumn{1}{c|}{\textbf{Mail Libraries}} \\
			\hline
			PHP & {{PEAR Mail\tablefootnote{PEAR Mail Website: https://pear.php.net/package/Mail}, PHPMailer\tablefootnote{PHPMailer Website:\\ https://github.com/PHPMailer/PHPMailer}, Swiftmailer\tablefootnote{Swiftmailer Website: http://swiftmailer.org/}}}\\
			\hline
			Python & SMTPLib with email.header.Header\tablefootnote{instead of using email.parser.Parser to parse the header}\\
			\hline
			Java & Apache Commons E-Mail\tablefootnote{Apache Commons E-Mail: https://commons.apache.org/proper/commons-email/}\\
			\hline
			Ruby & Ruby Mail \textgreater{}= 2.6\tablefootnote{Ruby Mail Website: https://rubygems.org/gems/mail}\\
			\hline
			WordPress & Contact Form 7\tablefootnote{Contact Form 7 Download: https://wordpress.org/plugins/contact-form-7/}\\
			\hline
		\end{tabular}
		\caption[\titlecap{Mail libraries that prevent e-mail header injection}]{Mail libraries that prevent e-mail header injection.}
		\label{tab:maillib}
	\end{table}
	\item Use a Content Management System (CMS) \\
	Content management systems such as WordPress and Drupal include libraries and plugins to prevent \ehi. Thus, websites built with such CMS' are usually resistant to these attacks. However, it is advised to use the correct \email plugin, as not all plugins might be secure.
	An example of a secure plug-in is included as part of Table~\ref{tab:maillib}.

	\item Input Validation\\
	If neither of the two options are feasible (website being an in-house production, or due to lack of support infrastructure), developers can choose to perform proper input sanitization. Sanitization should be done keeping in mind RFC5322~\cite{rfc5322}, and care must be taken to ensure that all edge cases are taken into account.

### 2016-10-24 Results/analysis.tex
almost at 13 pages, need to bering it to 9

\begin{itemize}
	\item \Email Header Injections with both \texttt{bcc} and \texttt{x-check} headers\\
	  These represent the scenario where an attacker can inject multiple headers into the \emails. We can see that 65.65\% of the received \texttt{bcc} header injected \emails are also susceptible to being injected with additional headers.
      % Adam: What is the exact percentage? We should use that rather than an approximate number - DONE.

@@

	\item Total successful injections\\
	  This represents the total number of successful injections. This includes the \ehi with \texttt{bcc} header\,(1), \texttt{To} header injections alone\,(3), and Unique \texttt{x-check} headers found in \texttt{nuser} \emails\,(7). A total of \success vulnerabilities were found by our system.

>>>>

\begin{itemize}
	\item \Email Header Injections with both \texttt{bcc} and \texttt{x-check} headers\\
	  These represent the scenario where an attacker can inject multiple headers into the \emails. We can see that 54\% of the received \texttt{bcc} header injected \emails are also susceptible to being injected with additional headers.
      % Adam: What is the exact percentage? We should use that rather than an approximate number - DONE.

@@

	\item Total successful injections\\
	  This represents the total number of successful injections. This includes the \ehi with \texttt{bcc} header\,(1), \texttt{To} header injections\,(3), and Unique \texttt{x-check} headers found in \texttt{nuser} \emails\,(7). A total of \success vulnerabilities were found by our system.

### 2016-10-24 Results/disclosure.tex
updated with new email
updated for WWW paper
added virus email attachments section
almost at 13 pages, need to bering it to 9

\subsection{Responsible Disclosure of Discovered Vulnerabilities}
After we discovered an \ehi vulnerability on a particular website, we attempted to notify the developers of the vulnerable web application, along with a brief description of the vulnerability.
We chose to \email the following mailboxes, following the rules specified in RFC~2142~\cite{rfc2142}:
% Adam: don't we use \texttt for all the email addresses in the paper? We should use the same thing here - DONE.
\begin{itemize}
	\item \texttt{security@domain.com} - Used for Security bulletins or queries.
	\item \texttt{admin@domain.com} - Used to contact the administrator of a website.
	\item \texttt{webmaster@domain.com} - Synonym for administrator, same functionality as admin.
\end{itemize}

% Adam: sai, is this number up-to-date? 
Out of the \domains\ vulnerable domains found, only \emailedDefaultmailbox websites had the mailboxes able to receive \emails. For the remaining domains, we used the \texttt{whois}~\cite{whois} data to find the contact details of the owner and then \emailed them. The number of emails we sent and the number of developer responses we received is shown in Table~\ref{tab:devresp}.

\begin{table}[tbp]
\centering
\begin{tabular}{|c|c|c|}
	\hline
	\multicolumn{1}{|p{2cm}}{\centering \textbf{Notified websites}} &
	\multicolumn{1}{|p{2cm}|}{\centering \textbf{Developer Responses}} &
	\multicolumn{1}{p{2cm}|}{\centering \textbf{Confirmed discoveries}}\\
	\hline
	\domains\ & \responses & \confirmed \\
	\hline
\end{tabular}
	\caption[\titlecap{}]{Responsible disclosure of the discovered vulnerabilities to developers and the number of received responses.}
	\label{tab:devresp}
\end{table}

% Adam: did we get updated notifications? - nope. DONE.
We received \responses developer responses, confirming \confirmed discovered vulnerabilities. Two of the developers fixed the vulnerability on their website.
% is this done? 1 additional email asking for more information, but no confirmation.
From our research, it is clear that \ehi is quite widespread as a vulnerability, appearing on \successDelta\ of forms that we were able to perform automated attacks on. This value acts as a \emph{lower bound} for prevalence of \ehi vulnerability, and can quite easily be larger if the attacks were broader, crafted for the individual web application, and  less automated.

>>>>

\subsection{Responsible Disclosure of Discovered Vulnerabilities}
After we discovered an \ehi vulnerability on a particular website, we attempted to notify the developers of the vulnerable web application, along with a brief description of the vulnerability.
We chose to \email the following mailboxes, following the rules specified in RFC~2142~\cite{rfc2142}:
\begin{itemize}
	\item \texttt{security@domain.com} - Security bulletins or queries.
	\item \texttt{admin@domain.com} - The administrator of a website.
	\item \texttt{webmaster@domain.com} - Synonym for administrator, same functionality as admin.
\end{itemize}

Out of the \domains\ vulnerable domains found, only \emailedDefaultmailbox websites had the mailboxes able to receive \emails. For the remaining domains, we used the \texttt{whois}~\cite{whois} data to find the contact details of the owner and then \emailed them. The number of emails we sent and the number of developer responses we received is shown in Table~\ref{tab:devresp}.

\begin{table}[tbp]
\centering
\normalsize
\begin{tabular}{|c|c|c|}
	\hline
	\multicolumn{1}{|p{2cm}}{\centering \textbf{Notified websites}} &
	\multicolumn{1}{|p{2cm}|}{\centering \textbf{Developer Responses}} &
	\multicolumn{1}{p{2cm}|}{\centering \textbf{Confirmed discoveries}}\\
	\hline
	\domains\ & \responses & \confirmed \\
	\hline
\end{tabular}
	\caption[\titlecap{}]{Responsible disclosure of the discovered vulnerabilities to developers and the number of received responses.}
	\label{tab:devresp}
\end{table}

% Adam: did we get updated notifications? - updated. DONE.
We received \responses developer responses, confirming \confirmed discovered vulnerabilities. Four of the developers fixed the vulnerability on their website.
% is this done? 1 additional email asking for more information, but no confirmation.
From our research, it is clear that \ehi is quite widespread as a vulnerability, appearing on \successDelta\ of forms that we were able to perform automated attacks on. This value acts as a \emph{lower bound} for prevalence of \ehi vulnerability, and can quite easily be larger if the attacks were broader, crafted for the individual web application, and  less automated.

### 2016-10-24 Results/virus_data.tex
almost at 13 pages, need to bering it to 9

To do this, we passed the \totalattachmentcount attachments we received to VirusTotal~\cite{virustotal} -- an online virus and malware scanner that checks for the presence of malware by running 40+ virus scanners on the uploaded files. We found that out of the \totalattachmentcount attachments, \totalvirusemails \emails contained malicious attachments, out of which \totalvirusattachmentcount were found to be from unique domains. 
%It is to be noted that none of these domains were found on the spam analysis we did earlier, indicating that if these could be exploited, we could send emails with malicious attachments to other people using these servers.

>>>>

To do this, we passed the \totalattachmentcount attachments we received to VirusTotal~\cite{virustotal} -- an online virus and malware scanner that checks for the presence of malware by running 40+ virus scanners on the uploaded files. We found that out of the \totalattachmentcount attachments, \totalvirusemails \emails contained malicious attachments, out of which \totalvirusattachmentcount were from unique domains. 
%It is to be noted that none of these domains were found on the spam analysis we did earlier, indicating that if these could be exploited, we could send emails with malicious attachments to other people using these servers.

### 2016-10-24 System/proof_of_concept.tex
almost at 13 pages, need to bering it to 9

\subsection{Validation}
To validate our system, we constructed three sets of web applications in PHP, Python, and Ruby. Each of these applications was a simple web application that accepted user input to construct and send an \Email.

@@

\begin{lstlisting}[language=HTML,caption={HTML page for showcasing
      \ehi, a simple front-end for our
      examples.},label={code:html}, float]
<!doctype html>
<html lang="en">
<head>
<meta charset="utf-8">
<meta name="author" content="XYZ">
<title>Mock Email</title>
</head>
<body>
<form action="{path-to-back-end}" method="post">
<input type="text" placeholder="Email" name="email" id="\email"><br>
<textarea name="msg" rows="20" cols="120"></textarea>
<input type="submit" value="Email Me!">
</form>
</body>
</html>
\end{lstlisting}
\input{Background/ruby}

>>>>

To validate our system, we constructed three sets of web applications in PHP, Python, and Ruby. Each of these applications was a simple web application that accepted user input to construct and send an \Email.

@@

\begin{lstlisting}[language=HTML,caption={HTML page for showcasing
      \ehi, a simple front-end for our
      examples.},label={code:html}, float]
<!doctype html>
<html lang="en">
<head>
<meta charset="utf-8">
<meta name="author" content="XYZ">
<title>Mock Email</title>
</head>
<body>
<form action="script-path" method="post">
<input type="text" name="email">
<textarea name="msg"></textarea>
<input type="submit" value="Email Me!">
</form></body></html>
\end{lstlisting}
\input{Background/ruby}

### 2016-10-24 introduction.tex
almost at 13 pages, need to bering it to 9

\section{Introduction}
The World Wide Web has single-handedly brought about a change in the way we use computers. The ubiquitous nature of the web has made it possible for anyone to access information and services anywhere and on multiple devices such as phones, laptops, personal digital assistants, TVs, and cars. This access has ushered in an era of web applications which depend on user input. 
While the rapid pace of development has improved the speed of information dissemination, it comes at a cost. As users move more and more of their personal and financial information to web applications, attackers are responding by using web application vulnerabilities to access this lucrative data.

>>>>

\section{Introduction}
The World Wide Web has single-handedly brought about a change in the way we use computers. The ubiquitous nature of the web has made it possible for anyone to access information and services anywhere and on multiple devices such as phones, laptops, TVs, and cars. This access has ushered in an era of web applications which depend on user input. 
While the rapid pace of development has improved the speed of information dissemination, it comes at a cost. As users move more and more of their personal and financial information to web applications, attackers are responding by using web application vulnerabilities to access this lucrative data.

### 2016-10-24 rel_work.tex
almost at 13 pages, need to bering it to 9

The first documented article dates to over a decade ago; a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how this vulnerability existed in the reference implementation of the mail function in PHP, and how it can be exploited. Following this, we found other blog posts~\cite{Calin, DK, Injection2, Nicol, Pope}, each describing how to exploit the vulnerability by using newlines to camouflage headers inside user input. A wiki entry~\cite{Injection} also describes the ways to prevent such an attack. However, none of these articles have performed these attacks against real-life websites.

Another blog post written by user Voxel@Night on Vexatious Tendencies~\cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, \texttt{Contact Form}, with a proof of concept\footnotemark. It also showcases the vulnerable code in the plugin that causes this vulnerability to be present. However, this article targets just one plugin and does not aim to find the prevalence of said plugin usage. Neither does it inform the creators of the plugin to fix the discovered vulnerability.
\footnotetext{Note that this plugin is used actively on 300,000 websites (according to~\cite{BestWebSoft2016}), but is yet to be fixed.}
The vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook: Discovering and Exploiting Security Flaws}''~\cite{stuttard2011web}. The book, however, does not go into detail on either the attack or the ways to mitigate such an attack. Our work, on the other hand discusses the means to mitigate the attack. We also describe, in detail, the payloads that can be used and the need for varying the payloads (Section~\ref{Comp:Fuzzer:mp}).

>>>>

The first documented article dates to over a decade ago; a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo| describing how this vulnerability existed in the reference implementation of the mail function in PHP, and how it can be exploited. Following this, we found other blog posts~\cite{Calin, DK, Injection2, Nicol, Pope}, each describing how to exploit the vulnerability by using newlines to camouflage headers inside user input. A wiki entry~\cite{Injection} also describes the ways to prevent such an attack. However, none of these articles have performed these attacks against real-life websites.

Another blog post written by user \lstinline|Voxel@Night|~\cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, \texttt{Contact Form}, with a proof of concept\footnotemark. It also showcases the vulnerable code in the plugin that causes this vulnerability to be present. However, this article targets just one plugin and does not aim to find the prevalence of said plugin usage. Neither does it inform the creators of the plugin to fix the discovered vulnerability.
\footnotetext{Note that this plugin is used actively on 300,000 websites (according to~\cite{BestWebSoft2016}), but is yet to be fixed.}
The vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook: Discovering and Exploiting Security Flaws}''~\cite{stuttard2011web}. The book, however, does not go into detail on either the attack or the ways to mitigate such an attack. Our work, on the other hand discusses the means to mitigate the attack. We also describe, in detail, the payloads that can be used and the need for varying the payloads (Section~\ref{Comp:Fuzzer:mp}).
